\chapter{数学公式}

\section{Inline 公式}

由于输入便捷, \mintinline{text}{$...$} 更受到欢迎.

\subsection{\protect\verbum{math} 环境}

使用 \mintinline{text}{math} 环境：

\inputlatexcode{../examples/formulas/inline-quad1.tex}

\subsection{\protect\verbum*{(}...\protect\verbum*{)} 环境}

使用 \mintinline{text}{\(...\)} 环境：

\inputlatexcode{../examples/formulas/inline-quad2.tex}

\subsection{\protect\verbum{\$}...\protect\verbum{\$} 环境}

使用 \mintinline{text}{$...$} 环境：

\inputlatexcode{../examples/formulas/inline-quad3.tex}

\section{Displayed 公式}

推荐使用 \mintinline{text}{\[...\]}, 在处理间距更好一些.

\subsection{\protect\verbum{displaymath} 环境}

使用 \mintinline{text}{displaymath} 环境：

\inputlatexcode{../examples/formulas/displayed-quad1.tex}

\subsection{\protect\verbum*{[}...\protect\verbum*{]} 环境}

使用 \mintinline{text}{\[...\]} 环境：

\inputlatexcode{../examples/formulas/displayed-quad2.tex}

\subsection{\protect\verbum{\$\$}...\protect\verbum{\$\$} 环境}

使用 \mintinline{text}{$$...$$} 环境：

\inputlatexcode{../examples/formulas/displayed-quad3.tex}

\section{自动编号: \protect\verbum{equation} 环境}

\mintinline{text}{equantion，align} 等环境默认是自动编号的，如果不需要编号则使用 \mintinline{text}{equation*，align*} 等环境。
对应多行公式内容，如果不需要编号则使用 \mintinline{text}{\\notag}。

\inputlatexcode{../examples/formulas/numbering-equations.tex}

\section{多行公式}

\subsection{\protect\verbum{multline} 环境}

\inputlatexcode{../examples/formulas/amsmath-multline.tex}

\subsection{\protect\verbum{gather} 环境}

\inputlatexcode{../examples/formulas/amsmath-gather.tex}

\subsection{\protect\verbum{align} 环境}

\inputlatexcode{../examples/formulas/amsmath-align.tex}

\subsection{\protect\verbum{split} 环境}

\inputlatexcode{../examples/formulas/amsmath-split.tex}

\subsection{\protect\verbum{flalign} 环境}

\inputlatexcode{../examples/formulas/amsmath-flalign.tex}

\subsection{\protect\verbum{alignat} 环境}

\inputlatexcode{../examples/formulas/amsmath-alignat.tex}

\inputlatexcode{../examples/formulas/amsmath-alignat-text.tex}

注意: \mintinline{text}{&&}实际上是\mintinline{text}{& &}。 这里增加了一列水平间距，使得文字能够左对齐。

\subsection{\protect\verbum{algined}、\protect\verbum{gathered} 和 \protect\verbum{alignedat} 环境}

Used for an aligned block within a math environment. This can be displayed math or in-line math.

\inputlatexcode{../examples/formulas/amsmath-aligned.tex}

\section{文本}

To insert some text into a formula, standard LaTeX provides the \mintinline{text}{\mbox} command. 
amsmath offers further commands:

\begin{description}
  \item \mintinline{text}{\text{words}}: inserts text within a math formula. The size is adjusted according to the current math style, that is, \mintinline{text}{\text} produces smaller text within subscripts or superscripts.
  \item \mintinline{text}{\intertext{text}}: suspends the formula, the text follows in a separate paragraph, then the multi-line formula is resumed, keeping the alignment. Use it for longer text.
\end{description}

\inputlatexcode{../examples/formulas/intertext.tex}

\section{Cases}

\inputlatexcode{../examples/formulas/cases-left.tex}

\mintinline{text}{rcase} 是自定义的环境：

\begin{minted}{latex}
\newenvironment{rcase}
  {\left.\begin{aligned}}
  {\end{aligned}\right\rbrace}
\end{minted}

\inputlatexcode{../examples/formulas/cases-right.tex}

\begin{remark*}
\mintinline{text}{\,} Include a thin space in math mode.
\end{remark*}
